---
title: "SarahGDataGraphicRedone"
author: "Sarah Gillespie"
date: "4/3/2019"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###### My process:
###### I took the invitation to recreate an data graphic from [an article redesigning past Economist graphs](https://medium.economist.com/mistakes-weve-drawn-a-few-8cdd8a42d368). This data graphic goes with a March 2017 article titled ["Science remains male-dominated"](https://www.economist.com/science-and-technology/2017/03/11/science-remains-male-dominated).

###### I copied the data into Google Sheets, removed the top row, and relabeled the columns to not have spaces and to be more accurate to their data. Then I downloaded the file as a CSV and uploaded it into Rstudio.

###### The article focuses on the overall publication and patent proportion by country (rather than in-depth analysis by field on the orginal graphic), so I thought my ggplot graphic should have a similar focus. I found the average of percent of publications by women across all fields, weighing each field equally. This might not be ideal statistics but it was the best I could do with the limited data. I kept the inventor proportion the same because filing a patent has a different process and requirements than publishing a reseach paper in academia.

###### I created a data frame using dyplr functions and reshape2's melt, then made a grouped bar plot using ggplot2 and ggthemes.

###### One problem with this data graphic is the order of the countries. I wish they were in descending order starting with the country with the highest proportion of women producing STEM reseach papers, but instead it is in reverse alphabetical order by country.

```{r EData, echo=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(ggrepel)
library(reshape2)

EconomistWomenResearch <- read_csv("EconomistWomenResearch.csv")

EconomistWomenResearch2 <- EconomistWomenResearch %>%
  mutate(STEM_Papers = ((Health_sciences + Physical_sciences + Engineering + Computer_science_math)/4)) %>%
  select(Country, WomenInventors, STEM_Papers)

EconomistWomenResearch2$WomenInventors <- EconomistWomenResearch2$WomenInventors * 100

EconomistWomenResearch2$STEM_Papers <- EconomistWomenResearch2$STEM_Papers * 100

#using melt from reshape2
meltedEWR2 <- melt(data = EconomistWomenResearch2, id.vars = "Country", measure.vars = c("WomenInventors", "STEM_Papers"))
```

```{r EPlot, echo=FALSE}
# plot my data
ggplot(meltedEWR2, aes(y=value, x=Country)) + 
  geom_bar(aes(fill = variable), width = 0.6, position = position_dodge(width=0.6), stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Papers and Patents Published by Women") +
  labs(y="Percent published by women") + 
  theme_economist() +
  coord_flip() +
  scale_fill_manual(values=c("#00CC00", "#0000FF"))

```

###### Notes on data:
###### Papers published	Indexed in Scopus			
###### Inventors	Who filed patent applications			
				
###### Sources: "Gender in the Global Research Landscape" by Elsevier; The Economist				

^[[Github Repository](https://github.com/SarahGillespie/EconomistGraphicRedone)]
